OpenIDEO: Diversity of Immediate Inspirations --> Shortlist
========================================================

```{r preliminaries}
library(lme4)
library(arm)
library(ggplot2)
library(psych)
library(dplyr)

#load the data
path = "/Users/joelc/Dropbox/Research/dissertation/OpenIDEO/Pipeline/Challenge_and_High-level_Data/iPython intermediate inputs and outputs/ConceptLevel_AfterDistanceAndControlsAndDiversity.csv"
data = read.csv(path,header=TRUE,sep=',')
data <- subset(data,insp_dist_count > 1) # drop the single-insp and no-insp cases
```

# Descriptives

stats
```{r descriptive statistics}
describe(data[c('shortlist','comments_preshortlist','num_shortlisted_sources','insp_dist_z_insp_mean','insp_div_mean')])
```

intercorrelations
```{r intercorrelations}
library(Hmisc) # note: 'describe' from the psych package won't work past this point
rcorr(as.matrix(data[c('shortlist','comments_preshortlist','num_shortlisted_sources','insp_dist_z_insp_mean','insp_div_mean')]))
```

plot distribution of diversity
```{r fig.width=7, fig.height=6}
ggplot(data, aes(insp_div_mean)) + 
  geom_histogram(fill=NA,color="black") + 
  theme_bw()
```

scatterplot matrix
```{r fig.width=7, fig.height=6}
pairs(~shortlist+comments_preshortlist+num_shortlisted_sources+insp_dist_z_insp_mean+insp_div_mean,data=data,
      panel=function(x,y){
        points(x,y)
        abline(lm(y~x),lty=2)
        lines(lowess(x,y))
        },
      diag.panel=function(x){
        par(new=T)
        hist(x,main="",axes=F)
        }
      )
```

plot binnned Pr(shortlist) vs mean diversity to guide model-building
```{r fig.width=6, fig.height=4}
data$bin_divMean_4 <- cut2(data$insp_div_mean, g=4)

# summarize the data for the bins
summarized <- data %.% 
  group_by(bin_divMean_4) %.% 
  summarise(propShortlist=mean(shortlist), 
            meanVal=mean(insp_div_mean),
            sdVal=sd(insp_div_mean),
            n=length(shortlist))

# compute standard errors
summarized$error_propShortlist <- sqrt(summarized$propShortlist*(1-summarized$propShortlist)/summarized$n)
summarized$error_meanVal <- summarized$sdVal/sqrt(summarized$n)

ggplot(summarized) + 
  geom_errorbar(mapping=aes(x=meanVal, ymin=propShortlist-1.95* error_propShortlist, ymax=propShortlist+1.95* error_propShortlist),width=0.0) + 
  geom_errorbarh(aes(x=meanVal,y=propShortlist,xmin=meanVal-1.95*error_meanVal, xmax=meanVal+1.95* error_meanVal),height=0.0) + 
  geom_point(mapping=aes(x=meanVal,y=propShortlist), size=3, shape=21, fill="white") + 
  labs(x="Mean pairwise distance",y="Pr(shortlist)") + 
  scale_x_continuous(breaks=seq(-0.45,0,.1),limits=c(-0.45,0)) + 
  scale_y_continuous(breaks=seq(0,.3,.1),limits=c(0,.3)) + 
  theme_bw()
```

# MODEL TIME!

## Fully unconditional

the model

```{r modelNull}
fit.div.insp.null = glmer(shortlist ~ (1|authorURL) + (1|challenge), data=data, family=binomial)
summary(fit.div.insp.null)
confint.merMod(fit.div.insp.null,method='Wald')
```

### test sig. of variance components

challenge
```{r testREchall}
fit.div.insp.auth = glmer(shortlist ~ (1|authorURL), data=data, family=binomial)
anova(fit.div.insp.auth,fit.div.insp.null,test='LRT')
```

author
```{r testREAuthor}
fit.div.insp.chall = glmer(shortlist ~ (1|challenge), data=data, family=binomial)
anova(fit.div.insp.chall,fit.div.insp.null,test='LRT')
```

## Controls

```{r modelControls}
fit.div.insp.controls = glmer(shortlist ~ (1|authorURL) + (1|challenge) + num_shortlisted_sources + comments_preshortlist, data=data, family=binomial)
summary(fit.div.insp.controls)
confint.merMod(fit.div.insp.controls,method='Wald')
anova(fit.div.insp.null,fit.div.insp.controls,test='LRT') # yes, chisq(2) = 61.14, p < .001
```

## Mean Diversity
```{r modelDiversity}
data$insp_div_mean_rescaled <- data$insp_div_mean*10 #rescale for easier interpretation of coefficient
fit.div.insp.divmean = glmer(shortlist ~ (1|authorURL) + (1|challenge) + num_shortlisted_sources + comments_preshortlist + insp_div_mean_rescaled, data=data, family=binomial)
summary(fit.div.insp.divmean)
confint.merMod(fit.div.insp.divmean,method='Wald')
anova(fit.div.insp.controls,fit.div.insp.divmean,test='LRT') # add anything over control?
```

any problem variation?
```{r modelDiversityRE}
fit.div.insp.divmean.RE = glmer(shortlist ~ (1|authorURL) + (insp_div_mean_rescaled|challenge) + insp_div_mean_rescaled + num_shortlisted_sources + comments_preshortlist, data=data.div.insp, family=binomial)
summary(fit.div.insp.divmean.RE)
confint.merMod(fit.div.insp.divmean.RE,method='Wald')
anova(fit.div.insp.divmean,fit.div.insp.divmean.RE,test='LRT') 
```

# outlier influence
influence.div.insp.divmean = influence.ME(fit.div.insp.divmean,obs=TRUE) #drop individual cases, not higher-level units
dfbetas.divmean = dfbetas.estex(influence.div.insp.divmean,parameters='insp_div_mean')
boxplot(dfbetas.divmean,ylab="DFBETAS for mean diversity")

### REPEAT DISTANCE ###
# base
fit.div.insp.distmean = glmer(shortlist ~ (1|authorURL) + (1|challenge) + insp_dist_z_insp_mean + num_shortlisted_sources + comments_preshortlist, data=data.div.insp, family=binomial)
summary(fit.div.insp.distmean) # effect is in the same direction, of similar size, but with more noise (now "marginal")
confint.merMod(fit.div.insp.distmean,method='Wald') # 95% CI = [-0.91,0.07]

# add (control for?) diversity
fit.div.insp.distmean.divmean = glmer(shortlist ~ (1|authorURL) + (1|challenge) + insp_dist_z_insp_mean + insp_div_mean_rescaled + num_shortlisted_sources + comments_preshortlist, data=data.div.insp, family=binomial)
summary(fit.div.insp.distmean.divmean)
confint.merMod(fit.div.insp.distmean.divmean,method='Wald')

# not much point, but see if there's an interaction between distance and diversity? (bivariate linear r = ~.3)
data.div.insp$insp_distmeanXdivmean = data.div.insp$insp_dist_z_insp_mean * data.div.insp$insp_div_mean # create interaction term
fit.div.insp.distmean.divmean.inter = glmer(shortlist ~ (1|authorURL) + (1|challenge) + insp_dist_z_insp_mean + insp_div_mean_rescaled + insp_distmeanXdivmean + num_shortlisted_sources + comments_preshortlist, data=data.div.insp, family=binomial)
summary(fit.div.insp.distmean.divmean.inter)
confint.merMod(fit.div.insp.distmean.divmean.inter,method='Wald')

anova(fit.div.insp.controls,fit.div.insp.distmean,fit.div.insp.distmean.divmean, fit.div.insp.distmean.divmean.inter,test='LRT')
