OpenIDEO Variety Analysis (K=400[6],t=60)
========================================================

Load data and packages
```{r loadStuff, echo=FALSE}
path = "/Users/joelc/Dropbox/Research/dissertation/OpenIDEO/Pipeline/Validation/FINAL_malletLDA/ConceptLevel_AfterDistanceAndControlsAndDiversityAndCorrectedDiscreteVariety_K400-6_T60.csv"
data.var.k400t60 = read.csv(path)
data.var.k400t60 <- subset(data.var.k400t60, both_numSources > 0)
library(lme4)
library(psych)
```

# Descriptives first
## Descriptive statistics
```{r descriptives}
describe(data.var.k400t60[c('shortlist','comments_preshortlist','num_shortlisted_sources','both_numSources','both_sourceVariety')])
```

## Intercorrelations
```{r correlations}
library(Hmisc) # watch out, there is a conflicting named function "describe" - we want the one from psych
rcorr(as.matrix(data.var.k400t60[c('shortlist','comments_preshortlist','num_shortlisted_sources','both_numSources','both_sourceVariety')]))
```

# Models
# Null and control

Null
```{r modelNull}
fit.var.k400.t60.both.null = glmer(shortlist ~ (1|authorURL) + (1|challenge_x), data=data.var.k400t60, family=binomial)
summary(fit.var.k400.t60.both.null)
```

Test sig. of the random effects
```{r modelNullsigRandomEffects}
fit.var.k400.t60.both.null.authorsOnly = glmer(shortlist ~ (1|authorURL), data=data.var.k400t60, family=binomial)
fit.var.k400.t60.both.null.challOnly = glmer(shortlist ~ (1|challenge_x), data=data.var.k400t60, family=binomial)
anova(fit.var.k400.t60.both.null.authorsOnly,fit.var.k400.t60.both.null,test='LRT') # is the challenge random-effect sig?
anova(fit.var.k400.t60.both.null.challOnly,fit.var.k400.t60.both.null,test='LRT') # is the author random-effect sig?
```

Control
```{r modelControl}
fit.var.k400.t60.both.controls = glmer(shortlist ~ (1|authorURL) + (1|challenge_x) + comments_preshortlist + num_shortlisted_sources + both_numSources, data=data.var.k400t60, family=binomial)
summary(fit.var.k400.t60.both.controls)
```

LRT to compare against
```{r LRTControlvsNull}
anova(fit.var.k400.t60.both.null,fit.var.k400.t60.both.controls,test='LRT')
```

Confidence intervals
```{r CIControl}
confint.merMod(fit.var.k400.t60.both.controls,method='Wald')
```

# For real

Now our first model with just variety
```{r modelVarLinear}
fit.var.k400.t60.both.varLinear = glmer(shortlist ~ (1|authorURL) + (1|challenge_x) + comments_preshortlist + num_shortlisted_sources + both_numSources + both_sourceVariety, data=data.var.k400t60, family=binomial)
summary(fit.var.k400.t60.both.varLinear)
```

Confidence intervals
```{r CIVarLinear}
confint.merMod(fit.var.k400.t60.both.varLinear,method='Wald')
```

No real effect of variety, also confirmed by LRT that adding it to the model doesn't really improve our fit to the data
```{r LRTVarLinearVSControl}
anova(fit.var.k400.t60.both.controls,fit.var.k400.t60.both.varLinear,test='LRT')
```

Let's add a quadratic term now
```{r modelVarQuadr}
data.var.k400t60$both_sourceVariety.sq = data.var.k400t60$both_sourceVariety^2
fit.var.k400.t60.both.varQuadr = glmer(shortlist ~ (1|authorURL) + (1|challenge_x) + comments_preshortlist + num_shortlisted_sources + both_numSources + both_sourceVariety + both_sourceVariety.sq, data=data.var.k400t60, family=binomial)
summary(fit.var.k400.t60.both.varQuadr)
```

Notice the very wide confidence intervals
```{r CIVarQuadr}
confint.merMod(fit.var.k400.t60.both.varQuadr,method='Wald')
```

So there's a hint of a positive linear effect of variety with a deceleration function (basically an inverted-U effect).
BUT, it is marginal, and the model with these terms doesn't really fit better than control (the LRT is n.s., and the AIC is *slightly* larger)
```{r LRTVarQuadrVSControl}
anova(fit.var.k400.t60.both.controls,fit.var.k400.t60.both.varQuadr,test='LRT')
```
